Supporting Information: Modeling Monomer Interactions with Molecular Dynamics

### 2019-10-14 Ben_Manuscripts/catalysis/Supporting_Information.tex
Tandem catalysis SI updates

>>>>

  We extrapolated the final number of reacted catalytic groups by fitting a
  plateauing function of the form:
  \begin{equation}
  f(x) = M(1 - x^{-a})
  \label{eqn:plateau}
  \end{equation}
  where $M$ and $a$ are the asymptotic maximum function value and the rate of
  decay respectively. We believe this type of fit is necessary because the 
  number of hydrogen bond "reactions" continues to grow slowly over time even
  after long plateaus (see Figure~\ref{fig:reacted_all}).

  There are multiple regimes of growth in the number of hydrogen bond surrogate
  reactions. Since we are interested in the asymptotic value, $M$, of the plateau,
  we fit Equation~\ref{eqn:plateau} to the average growth curve starting after
  40 ns where the percent reacted head groups versus the log of time becomes
  consistently linear (see Figure~\ref{fig:loglog}).

%  Because the system is very slowly approaching a plateau, we found that 
%  an $x^{-a}$ power law dependence in Equation~\ref{eqn:plateau} provided 
%  a better fit to the data than an exponential dependence ($e^{-ax}$) 
%  (see Figure~\ref{fig:fit_comparison}).

  \begin{figure}
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{reacted_all.pdf}
  \caption{}\label{fig:reacted_all}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{loglog.pdf}
  \caption{}\label{fig:loglog}
  \end{subfigure}
%  \begin{subfigure}{0.325\textwidth}
%  \includegraphics[width=\textwidth]{fit_comparison.pdf}
%  \caption{}\label{fig:fit_comparison}
%  \end{subfigure}
  \caption{(a) Although the growth rate of total surrogate reactions decreases 
  with time, it is likely that the curves will not fully plateau on a time scale
  that we can reasonably simulate. (b) The growth rate appears to enter at least
  three distinct regimes shown approximately by the different colored regions. We
  fit Equation~\ref{eqn:plateau} to the last (green) regime. 
  %(c) A power law 
  %growth rate ($x^{-a}$) gives a superior fit to our simulation data compared to
  %an exponential growth rate ($e^{-ax}$).
  }\label{fig:plateau}
  \end{figure}

  We used bootstrapping to determine the mean value of $M$ with its associated
  uncertainty. The procedure is as follows:
  \begin{enumerate}
  	\item Randomly choose, with replacement, 4 of the curves in Figure~\ref{fig:reacted_all}.
  	\item Fit Equation~\ref{eqn:plateau} to the mean of the 4 curves to get the value of $M$.
  	\item Repeat 200 times to generate a distribution of $M$ values. 
  	\item Report mean and standard error of $M$ distribution.
  \end{enumerate}
  Note that this procedure is best performed with many more than 4 curves, however
  it should still yield a more realistic uncertainty than the typically very small
  error returned by the single non-linear least squares fit to the average.
